\newpage
\clearpage
\pagestyle{plain}
%\textbf{\huge Research Activities}\label{research_activity}
%\vspace{10mm}\\
%\begin{itemize}
\chapter{Research Activities} 
\label{research_activity}
\begin{enumerate}
	\Large
	\item[] Peer-Reviewed Journal Papers  (First author)
	\normalsize
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. “An Improvement of Scalar Multiplication by Skew Frobenius Map with Multi-Scalar Multiplication for KSS Curve”. In: \textit{IEICE Transactions} 100-A.9 (2017), pp. 1838-1845. \textsc{doi}: \href{https://doi.org/10.1587/transfun.E100.A.1838}{\texttt{10.1587/transfun.E100.A.1838}}.
	%	( Impact Factor (2017): 1.09)
	\normalsize
	\item\textbf{Md. Al-Amin Khandaker}, Taehwan Park, Yasuyuki Nogami, and Howon Kim. “A Comparative Study of Twist Property in KSS Curves of Embedding Degree 16 and 18 from the Implementation Perspective”. In: \textit{J. Inform. and Commun. Convergence Engineering} 15.2 (2017),  pp. 97-103. \textsc{doi}: \href{https://doi.org/10.6109/jicce.2017.15.2.97}{\texttt{10.6109/jicce.2017.15.2.97}}.
	%\end{enumerate}
	%\normalsize
	\vspace{10mm}
	\item[ ] \Large Peer-Reviewed International Conference Papers  (First author)
	\normalsize
	%\begin{enumerate}
	\item[ ] \Large LNCS Proceedings:
	\normalsize
	\item \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Loubna Ghammam, Sylvain Duquesne, Yasuyuki Nogami, and Yuta Kodera. “Efficient Optimal Ate Pairing at 128-Bit Security Level”. In: \textit{INDOCRYPT 2017}. Ed. by Arpita Patra
	and Nigel P. Smart. Vol. 10698. LNCS. Springer, Heidelberg, Dec. 2017, pp. 186–205. \textsc{doi}: \href{https://doi.org/10.1007/978-3-319-71667-1_10}{\texttt{10.1007/978-3-319-71667-1\_10}}. 	(Acceptance rate 19/75 $\approx$ 25\%)
	
	\item \textbf{Md. Al-Amin Khandaker}, Hirotaka Ono, Yasuyuki Nogami, Masaaki Shirase, and Sylvain Duquesne. ``An Improvement of Optimal Ate Pairing
	on KSS Curve with Pseudo 12-Sparse Multiplication". In: \textit{ICISC 2016}. Ed. by Seokhie Hong and Jong Hwan Park. Vol. 10157. LNCS. Springer, Heidelberg, Nov. 2016, pp. 208–219. \textsc{doi}: \href{https://doi.org/10.1007/978-3-319-53177-9_11}{\texttt{10.1007/978-3-31953177-9\_11}}. 
	(Acceptance rate 18/69 $\approx$ 26\%)
	
	\item \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, Hwajeong Seo, and Sylvain Duquesne. ``Efficient Scalar Multiplication for Ate Based Pairing over KSS Curve of Embedding Degree 18''. In: \textit{WISA 2016}. Ed. by Dooho Choi and Sylvain Guilley. Vol. 10144. LNCS. Springer, Heidelberg, Aug. 2016, pp. 221–232. \textsc{doi}: \href{https://doi.org/10.1007/978-3-319-56549-1\_19}{\texttt{10.1007/978-3-319-56549-1\_19}}.
	(Acceptance rate 31/61 $\approx$ 51\%)
	\vspace{5mm}
	%		\clearpage
	%(Acceptance rate 32/84 $\approx$ 38\%)
	\item[ ] \Large IEEE Xplore indexed:
	\normalsize
	\item \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Takuya Kusaka, and Yasuyuki Nogami. ``A Comparative Implementation of GLV Technique on KSS-16 Curve.'' In:  \textit{Sixth International Symposium on Computing and Networking, CANDAR 2018}, Gifu, Japan, Nov. 2018. [To appear]
	(Acceptance rate 28/77 $\approx$ 36\%)
	%		\item \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Takuya Kusaka, and Yasuyuki Nogami. ``A Comparative Implementation of GLV Technique on KSS-16 Curve.'' In:  \textit{Sixth International Symposium on Computing and Networking, CANDAR 2018}, Gifu, Japan, November 27-30, 2016. 2018, pp. ?–?. \textsc{doi}: \href{_}{\texttt{?}}. (Acceptance rate 28/77 $\approx$ 36\%)
	
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. “Isomorphic Mapping for Ate-Based Pairing over KSS Curve of Embedding Degree 18”. In: \textit{Fourth International Symposium on Computing and Networking, CANDAR 2016}, Hiroshima, Japan, Nov. 2016, pp. 629–634. \textsc{doi}: \href{https://doi.org/10. 1109/CANDAR.2016.0113}{\texttt{10.1109/\\CANDAR.2016.0113}}.
	
	\item  \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``A consideration of towering scheme for efficient arithmetic operation over extension field of degree 18''. In: \textit{19th International Conference on Computer and Information Technology, ICCIT 2016}, Dhaka, Bangladesh, Dec. 2016, pp. 276–281. \textsc{doi}: \href{https://doi.org/10.1109/ICCITECHN.2016.7860209}{\texttt{10.1109/ICCITECHN.2016.7860209}}.
	
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``An improvement of scalar multiplication on elliptic curve defined over extension field Fq2''. In: \textit{IEEE International Conference on Consumer Electronics-Taiwan, ICCE- TW 2016}, Nantou, Taiwan, May. 2016, pp. 1–2. \textsc{doi}: \href{https://doi.org/10.1109/ICCE-TW.2016.7520894}{\texttt{10.1109/ICCE-TW.\\2016.7520894}}.
	
	\vspace{5mm}
	%		\clearpage
	%(Acceptance rate 32/84 $\approx$ 38\%)
	\item[ ] \Large IEICE/IEIE sponsored:
	\normalsize
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``Frobenius Map and Skew Frobenius Map for Ate-based Pairing over KSS Curve of Embedding Degree 16 ''. In: \textit{International Technical Conference on Circuits / Systems, Computers and Communications, ITC-CSCC 2017},  Busan, Korea, Jul. 2017. IEIE.
	%\end{enumerate}
	
	
	\vspace{10mm}
	\clearpage
	\Large
	\item[] Peer-Reviewed Journal Papers  (Co-author)
	\normalsize
	
	%\begin{enumerate}
	\normalsize
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami. “Efficient Pairing-Based Cryptography on Raspberry Pi”. In: \textit{Journal of Communications (JCM)} 13.2 (2018), pp. 88–93. \textsc{doi}: \href{https://doi.org/10.12720/jcm.13.2.88-93}{\texttt{10.12720/\\jcm.13.2.88-93}}.
	
	\normalsize
	%\item Yuta Hashimoto,  \textbf{Md. Al-Amin Khandaker}, Yuta Kodera, Taehwan Park, Takuya Kusaka, Howon Kim, Yasuyuki Nogami, ``An Implementation of ECC with Twisted Montgomery Curve over 32nd Degree Tower Field on Arduino Uno.'' International Journal of Networking and Computing (IJNC), vol. 8, no. 2, pp. 341-350, 2018.\url{https://doi.org/10.15803/ijnc.8.2_341}
	\item Yuta Hashimoto, \textbf{Md. Al-Amin Khandaker}, Yuta Kodera, Taehwan Park, Takuya Kusaka, Howon Kim, and Yasuyuki Nogami. ``An Implementation of ECC with Twisted Montgomery Curve over 32nd Degree Tower Field on Arduino Uno''. In: \textit{International Journal of Networking and Computing (IJNC)} 8.2 (2018), pp. 341–350. \textsc{doi}: \href{https://doi.org/10.15803/ijnc.8.2_341}{\texttt{10.15803/ijnc.8.2\_341}}.
	
	\normalsize
	% \item Yuta kodera, Takeru miyazaki, \textbf{Md. Al-Amin Khandaker},  Md. Arshad ali, Takuya kusaka, Yasuyuki nogami and Satoshi uehara. ``Distribution of Digit Patterns in Multi-Value Sequence over the Odd Characteristic Field.'' IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, vol. E101.A, no. 9, Sep. 2018, pp. 1525-1536, 2018. \url{https://doi.org/10.1587/transfun.E101.A.1525}
	\item Yuta Kodera, Takeru Miyazaki, \textbf{Md. Al-Amin Khandaker}, Ali Md. Arshad, Takuya Kusaka, Yasuyuki Nogami, and Satoshi Uehara. ``Distribution of Digit Patterns in Multi-Value Sequence over the Odd Characteristic Field''. In: \textit{IEICE Transactions} 101-A.9 (2018), pp. 1525–1536. \textsc{doi}: \href{https://doi.org/10.1587/transfun.E101.A.1525}{\texttt{10.1587/transfun.\\E101.A.1525}}.
	
	%\item	Shunsuke Ueda, Ken Ikuta, Takuya Kusaka,  \textbf{Md. Al-Amin Khandaker}, Ali Md. Arshad, Yasuyuki Nogami. ``An Extended Generalized Minimum Distance Decoding for Binary Linear Codes on a 4-Level Quantization over an AWGN Channel.'' IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, vol. E101.A, no. 8, Aug. 2018, pp. 1235-1244, 2018. \url{https://doi.org/10.1587/transfun.E101.A.1235}
	\item Shunsuke Ueda, Ken Ikuta, Takuya Kusaka, \textbf{Md. Al-Amin Khandaker}, Ali Md. Arshad, and \\ Yasuyuki Nogami. ``An Extended Generalized Minimum Distance Decoding for Binary Linear Codes on a 4-Level Quantization over an AWGN Channel”. In: \textit{IEICE Transactions} 101-A.8 (2018), pp. 1235–1244. \textsc{doi}: \href{https://doi.org/10.1587/transfun.E101.A.1235}{\texttt{10.1587/transfun.E101.A.1235}}.
	
	%\item Shoma Kajitani, Yasuyuki Nogami, Shunsuke Miyoshi, Thomas Austin, \textbf{Md. Al-Amin Khandaker}, Nasima Begum, Sylvain Duquesne, ``Web-based Volunteer Computing for Solving the Elliptic Curve Discrete Logarithm Problem.'' International Journal of Networking and Computing (IJNC), vol. 6, no. 2, pp. 181-194, 2016.
	\item Shoma Kajitani, Yasuyuki Nogami, Shunsuke Miyoshi, Thomas Austin, \textbf{Md. Al-Amin Khandaker}, Nasima Begum, and Sylvain Duquesne. “Web-based Volunteer Computing for Solving the Elliptic Curve Discrete Logarithm Problem”. In: \textit{International Journal of Networking and Computing (IJNC) }6.2 (2016), pp. 181–194. \textsc{doi}: \href{https://doi.org/10.15803/ijnc.6.2_181}{\texttt{10.15803/ijnc.6.2\_181}}.
	
	%\end{enumerate}
	\vspace{10mm}
	\Large
	\item[] Peer-Reviewed International Conference Papers  (Co-author)
	%\begin{enumerate}
	\item[ ] \Large LNCS Proceedings:
	\normalsize
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Masaaki Shirase, Takuya Kusaka, and Yasuyuki Nogami. ``Efficient Ate-Based Pairing over the Attractive Classes of BN Curves''. In: \textit{WISA 2018}. [To appear in LNCS, Springer, Heidelberg],  Aug. 2018.
	(Acceptance rate 22/44 = 50\%)
	%	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Masaaki Shirase, Takuya Kusaka, and Yasuyuki Nogami. ``Efficient Ate-Based Pairing over the Attractive Classes of BN Curves''. In: \textit{WISA 2018}. To appear LNCS. Springer, Heidelberg,  Aug. 2018.  pp. ?–?. \textsc{doi}: \href{?}{\texttt{?}}. (Acceptance rate 22/44 = 50\%)
	
	\item Takuya Kusaka, Sho Joichi, Ken Ikuta, \textbf{Md. Al-Amin Khandaker},  Yasuyuki Nogami, Satoshi Uehara, Nariyoshi Yamai, and Sylvain Duquesne. ``Solving 114-Bit ECDLP for a Barreto-Naehrig Curve''. In: \textit{ICISC 2017}. Ed. by Howon Kim and Dong-Chan Kim. Vol. 10779. LNCS. Springer, Heidelberg, Oct. 2017, pp. 231–244. \textsc{doi}: \href{https://doi.org/10.1007/978-3-319-78556-1_13}{\texttt{10.1007/978-3-319-78556-1\_13}}.
	(Acceptance rate 20/70 $\approx$ 29\%)
	
	\item  Taehwan Park, Hwajeong Seo, Garam Lee,\textbf{ Md. Al-Amin Khandaker}, Yasuyuki Nogami, and Howon Kim. ``Parallel Implementations of SIMON and SPECK, Revisited". In: \textit{WISA 2017}. Ed. by Brent ByungHoon Kang and Taesoo Kim. Vol. 10763. LNCS. Springer, Heidelberg, Aug. 2017, pp. 283–294. \textsc{doi}: \href{https://doi.org/10.1007/978-3-319-93563-8_24}{\texttt{10.1007/978-3-319-93563-8\_24}}.  
	(Acceptance rate 27/53 $\approx$ 51\%).
	
	\vspace{5mm}
	%(Acceptance rate 32/84 $\approx$ 38\%)
	\item[ ] \Large IEEE Xplore indexed:
	\normalsize
	
	%		\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami. ``Consideration of Efficient Pairing Applying Two Construction Methods of Extension Fields.'' In:  \textit{Sixth International Symposium on Computing and Networking, CANDAR 2018}, Gifu, Japan, November 27-30, 2016. 2018, pp. ?–?. \textsc{doi}: \href{_}{\texttt{?}}.
	
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami. ``Consideration of Efficient Pairing Applying Two Construction Methods of Extension Fields.'' In:  \textit{Sixth International Symposium on Computing and Networking, CANDAR 2018}, Gifu, Japan, Nov. 2018. [To appear]
	
	\item Yuta Hashimoto, \textbf{Md. Al-Amin Khandaker}, Yuta Kodera, Taehwan Park, Takuya Kusaka, Howon Kim, and Yasuyuki Nogami. ``An ECC Implementation with a Twisted Montgomery Curve over Fq32 on an 8-Bit Microcontroller''. In: \textit{Fifth International Symposium on Computing and Networking, CANDAR 2017}, Aomori, Japan, Nov. 2017, pp. 445–450. \textsc{doi}: \href{https://doi.org/10.1109/CANDAR.2017.90}{\texttt{10.1109/CANDAR.2017.90}}.
	
	
	\item	Yuta Kodera, Takuya Kusaka, Takeru Miyazaki, \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, and Satoshi Uehara. ``An Efficient Implementation of Trace Calculation over Finite Field for a Pseudorandom Sequence''. In: \textit{Fifth International Symposium on Computing and Networking, CANDAR 2017}, Aomori, Japan, Nov. 2017, pp. 451–455. \textsc{doi}: \href{https://doi.org/10.1109/CANDAR.2017.86}{\texttt{10.1109/CANDAR.2017.86}}.
	
	\item Taehwan Park, Hwajeong Seo, \textbf{Md. Al-Amin Khandaker}, Yasuvuki Nogami, and Howon Kim. ``Efficient Parallel Simeck Encryption with GPGPU and OpenCL''. In: \textit{IEEE International Conference on Consumer Electronics-Taiwan, ICCE-TW 2018}, Taichung, Taiwan, May 2018, pp. 1–2. \textsc{doi}: \href{https://doi.org/10.1109/ICCE-China.2018.8448768}{\texttt{10.1109/ICCE-\\China.2018.8448768}}.
	
	\item Yuta Kodera, Takeru Miyazaki, \textbf{Md. Al-Amin Khandaker}, Ali Md Arshad, Yasuyuki Nogami, and Satoshi Uehara. ``Distribution of bit patterns on multi-value sequence over odd characteristics field''.  In: \textit{IEEE International Conference on Consumer Electronics-Taiwan, ICCE-TW 2017}, Taipei, Taiwan, Jun. 2017, pp. 137-138. \textsc{doi}: \href{https://doi.org/10.1109/ICCE-China.2017.7991033}{\texttt{10.1109/ICCE-China.2017.7991033}}.	
	
	\item Akihiro Sanada, Yasuyuki Nogami, Kengo Iokibe, \textbf{Md. Al-Amin Khandaker}. ``Security analysis of Raspberry Pi against Side-channel attack with RSA cryptography''. In: \textit{IEEE International Conference on Consumer Electronics-Taiwan, ICCE-TW 2017}, Taipei, Taiwan, Jun. 2017, pp. 287 - 288. \textsc{doi}: \href{https://doi.org/10.1109/ICCE-China.2017.7991108}{\texttt{10.1109/ICCE-China.2017.7991108}}.	
	
	\vspace{5mm}
	%(Acceptance rate 32/84 $\approx$ 38\%)
	\item[ ] \Large IEICE/IEIE sponsored:
	\normalsize
	\item Ken Ikuta, Sho Joichi, Kazuya Kobayashi, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami. ``A Study on the Parameter Size of the Montgomery Trick for ECDLP''. In: \textit{International Symposium on Information Theory and its Applications, ISITA 2018}, Singapore, Oct. 2018.  IEICE. (To appear in IEEE Xplore).
	
	\item Ken Ikuta, Sho Joichi, Kazuya Kobayashi, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami. ``A Study on the Parameter of the Distinguished Point Method in Pollard's Rho Method for ECDLP''. In: \textit{International Symposium on Information Theory and its Applications, ISITA 2018},  Singapore, Oct. 2018. IEICE. (To appear in IEEE Xplore).	
	
	\item Ken Ikuta, Takuya Kusaka, \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, and Thomas H. Austin. ``Estimation of computational complexity of Pollard's rho method based attack for solving ECDLP over Barreto-Naehrig curves''. In: \textit{32nd International Technical Conference on Circuits / Systems, Computers and Communications, ITC-CSCC 2017},  Busan, Korea, Jul. 2017. IEIE.
	%\end{enumerate}
	\vspace{10mm}
	\large
	\item [] \Large Domestic conferences (First author)
	\normalsize
	%\begin{enumerate}
	
	\item \textbf{Md. Al-Amin Khandaker}, Hirotaka Ono, Yuki Nanjo, Takuya Kusaka and Yasuyuki Nogami. ``Efficient Optimal-Ate Pairing on BLS-12 Curve Using Pseudo 8-Sparse Multiplication''. In: \textit{Computer Security Symposium  (CSS),  2017}, Yamagata, Oct. 2017, CD-ROM (3E1-4). 
	
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``Efficient Scalar Multiplication by Skew Frobenius Map with Multi-Scalar Multiplication for KSS Curve''. In: \textit{Symposium on Cryptography and Information Security (SCIS),  2017}, Okinawa, Jan. 2017, CD-ROM (B1-3). 
	%\end{enumerate}
	
	\vspace{10mm}
	\large
	\item[] \Large Domestic conferences (Co-author)
	\normalsize
	%\begin{enumerate}
			\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Masaaki Shirase, Takuya Kusaka, and Yasuyuki Nogami.
		``Attractive Classes of KSS Curves for Efficient Pairing''.
		In: {\it Symposium on Cryptography and Information Security 2019 (SCIS)}, Shiga, Jan. 2019.
	
	\item Yuki Nanjo,  \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, Yasuyuki \\Nogami. ``A Study on a Construction Method of Degree 18 Extension Field for Efficient Pairing over KSS Curves''. In: \textit{Computer Security Symposium  (CSS),  2018}, Nagano, Oct. 2018, CD-ROM (2A3-1). 
	%		\item Yuki Nanjo,  \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, Yasuyuki Nogami. ``A Study on a Construction Method of Degree 18 Extension Field for Efficient Pairing over KSS Curves''. In: \textit{Computer Security Symposium  (CSS),  2018}, CD-ROM. (??)
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Masaaki Shirase, Takuya Kusaka, and Yasuyuki Nogami.
	``Determining BLS Curves for Pairing over Efficient Tower of Extension Field''.
	In: {\it Technical Committee on Information Security (ISEC )}, Tokyo, May 2018,
	IEICE Tech. Rep., vol. 118, no. 30, ISEC2018-2, pp. 9-16, May 2018.
	
	\item  Hirotaka Ono, \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Toshifumi Matsumoto, Takuya Kusaka and Yasuyuki Nogami. ``An Implementation and Evaluation of ID-based Authentication on Raspberry Pi with Pairing Library''. In: \textit{Symposium on Cryptography and Information Security (SCIS),  2018}, Niigata, Jan. 2018, CD-ROM (4D2-1).  
	
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Yuta Kodera and Yasuyuki Nogami. ``Implementation method of the pairing over BN curve using two type of extension fields''. In: \textit{Symposium on Cryptography and Information Security (SCIS),  2018}, Niigata, Jan. 2018, CD-ROM (4D2-3).
	
	\item  Norito Jitsui, Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka and Yasuyuki Nogami. ``Efficient Elliptic Scalar Multiplication for Pairing-Based Cryptography over BLS48''. In:  \textit{Symposium on Cryptography and Information Security (SCIS),  2018}, Niigata, Jan. 2018,  CD-ROM (3B4-1).
	
	\item Yuki Nanjo,  \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and  Yasuyuki Nogami. ``The relation between the efficient sextic twist and constant of the modular polynomial for BN curve''. In: \textit{Computer Security Symposium  (CSS),  2017}, Yamagata, Oct. 2017, CD-ROM (3E1-3). 
	
\end{enumerate}
\normalsize
%\end{itemize}



