
\newpage
\pagestyle{plain}
\textbf{\huge Research Activities}\label{research_activity}
\vspace{10mm}\\
\begin{itemize}
\large
\item Journal Papers (Peer-Reviewed)
\normalsize
\begin{enumerate}
		
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``An Improvement of Scalar Multiplication by Skew Frobenius Map with Multi-Scalar Multiplication for KSS Curve.'' IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, vol. E100.A, no. 9, Sep. 2017, pp. 1838-1845, 2017. \url{https://doi.org/10.1587/transfun.E100.A.1838}
	
	\item \textbf{Md. Al-Amin Khandaker}, Taehwan Park, Yasuyuki Nogami, and Howon Kim. ``A Comparative Study of Twist Property in KSS Curves of Embedding Degree 16 and 18 from the Implementation Perspective.'' KIICE Journal of Information and Communication Convergence Engineering, vol. 15, no. 2, Jun. 2017, pp. 93-103, 2017. \url{https://doi.org/10.6109/jicce.2017.15.2.97}
	
	\item Yuki Nanjo,  \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami, ``Efficient Pairing-Based Cryptography on Raspberry Pi.'' Journal of Communications, vol. 13, no. 2, pp. 88-93, 2018.  \url{https://doi.org/10.12720/jcm.13.2.88-93} 
		
	\item Yuta Hashimoto,  \textbf{Md. Al-Amin Khandaker}, Yuta Kodera, Taehwan Park, Takuya Kusaka, Howon Kim, Yasuyuki Nogami, ``An Implementation of ECC with Twisted Montgomery Curve over 32nd Degree Tower Field on Arduino Uno.'' International Journal of Networking and Computing (IJNC), vol. 8, no. 2, pp. 341-350, 2018.
	\url{https://doi.org/10.15803/ijnc.8.2_341}
	
	\item Yuta kodera, Takeru miyazaki, \textbf{Md. Al-Amin Khandaker},  Md. Arshad ali, Takuya kusaka, Yasuyuki nogami and Satoshi uehara. ``Distribution of Digit Patterns in Multi-Value Sequence over the Odd Characteristic Field.'' IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, vol. E101.A, no. 9, Sep. 2018, pp. 1525-1536, 2018. \url{https://doi.org/10.1587/transfun.E101.A.1525}
	
	\item	Shunsuke Ueda, Ken Ikuta, Takuya Kusaka,  \textbf{Md. Al-Amin Khandaker}, Ali Md. Arshad, Yasuyuki Nogami. ``An Extended Generalized Minimum Distance Decoding for Binary Linear Codes on a 4-Level Quantization over an AWGN Channel.'' IEICE Transactions on Fundamentals of Electronics, Communications and Computer Sciences, vol. E101.A, no. 8, Aug. 2018, pp. 1235-1244, 2018. \url{https://doi.org/10.1587/transfun.E101.A.1235}
	
	\item Shoma Kajitani, Yasuyuki Nogami, Shunsuke Miyoshi, Thomas Austin, \textbf{Md. Al-Amin Khandaker}, Nasima Begum, Sylvain Duquesne, ``Web-based Volunteer Computing for Solving the Elliptic Curve Discrete Logarithm Problem.'' International Journal of Networking and Computing (IJNC), vol. 6, no. 2, pp. 181-194, 2016.
	\url{https://doi.org/10.15803/ijnc.6.2_181}
	
\end{enumerate}
\newpage
\item International conferences (Peer-Reviewed)
\normalsize
\begin{enumerate}
	
		\item \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Takuya Kusaka, and Yasuyuki Nogami. ``A Comparative Implementation of GLV Technique on KSS-16 Curve.'' Sixth International Symposium on Computing and Networking (CANDAR), 2018. IEEE. (Acceptance Ratio 28/77 $\approx$ 36\%)
	
	\item \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Loubna Ghammam, Sylvain Duquesne, Yasuyuki Nogami, and Yuta Kodera. ``Efficient optimal ate pairing at 128-bit security level.'' In: Patra A., Smart N. (eds) Progress in Cryptology (INDOCRYPT), 2017. Lecture Notes in Computer Science, vol 10698. Springer, Cham.
	\url{https://doi.org/10.1007/978-3-319-71667-1_10}.
	
	\item \textbf{Md. Al-Amin Khandaker}, Hirotaka Ono, Yasuyuki Nogami, Masaaki Shirase, and Sylvain Duquesne. ``An Improvement of Optimal Ate Pairing on KSS Curve with Pseudo 12-Sparse Multiplication.'' In: Hong S., Park J. (eds) Information Security and Cryptology (ICISC), 2016. Lecture Notes in Computer Science, vol 10157. Springer, Cham. \url{https://doi.org/10.1007/978-3-319-53177-9_11}.
	
		\item \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, Hwajeong Seo, and Sylvain Duquesne. ``Efficient Scalar Multiplication for Ate Based Pairing over KSS Curve of Embedding Degree 18.'' In: Choi D., Guilley S. (eds) Information Security Applications (WISA), 2016. Lecture Notes in Computer Science, vol 10144. Springer, Cham. \url{https://doi.org/10.1007/978-3-319-56549-1_19}. 
		%(Acceptance Ratio 32/84 $\approx$ 38\%)

	\item \textbf{Md. Al-Amin Khandaker}, and Yasuyuki Nogami. ``Isomorphic Mapping for Ate-Based Pairing over KSS Curve of Embedding Degree 18.'' Fourth International Symposium on Computing and Networking (CANDAR), 2016. IEEE. \url{https://doi.org/10.1109/CANDAR.2016.0113}.
	
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``An improvement of scalar multiplication on elliptic curve defined over extension field Fq2.'' IEEE International Conference on Consumer Electronics-Taiwan (ICCE-TW), 2016. IEEE. \url{https://doi.org/10.1109/ICCE-TW.2016.7520894}.
	
	\item \textbf{Md. Al-Amin Khandaker}, and Yasuyuki Nogami. ``Frobenius Map and Skew Frobenius Map for Ate-based Pairing over KSS Curve of Embedding Degree 16 .'' 32nd International Technical Conference on Circuits / Systems, Computers and Communications (ITC-CSCC), 2017. IEIE.
	
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and Yasuyuki Nogami. ``Consideration of Efficient Pairing Applying Two Construction Methods of Extension Fields.'' Sixth International Symposium on Computing and Networking (CANDAR), 2018. IEEE.
	
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Masaaki Shirase, Takuya Kusaka and Yasuyuki Nogami. ``Efficient Ate-Based Pairing over the Attractive Classes of BN Curves.'' Information Security Applications (WISA), 2018. To appear Lecture Notes in Computer Science. Springer, Cham. (Acceptance Ratio 22/44 = 50\%)
	
	\item	Yuta Hashimoto, \textbf{Md. Al-Amin Khandaker}, Yuta Kodera, Taehwan Park, Takuya Kusaka, Howon Kim and Yasuyuki Nogami. ``An ECC Implementation with a Twisted Montgomery Curve over Fq32 on an 8-Bit Microcontroller.'' Fifth International Symposium on Computing and Networking (CANDAR), 2017. IEEE. \url{https://doi.org/10.1109/CANDAR.2017.90}.
	
	\item Taehwan Park, Hwajeong Seo, \textbf{Md. Al-Amin Khandaker}, Yasuvuki Nogami, Howon Kim. ``Efficient Parallel Simeck Encryption with GPGPU and OpenCL.'' IEEE International Conference on Consumer Electronics-Taiwan (ICCE-TW), 2018. IEEE.  \url{https://doi.org/10.1109/ICCE-China.2018.8448768}.
	
	\item Yuta Kodera, Takeru Miyazaki, \textbf{Md. Al-Amin Khandaker}, Ali Md Arshad, Yasuyuki Nogami, and Satoshi Uehara. ``Distribution of bit patterns on multi-value sequence over odd characteristics field.'' IEEE International Conference on Consumer Electronics-Taiwan (ICCE-TW), 2017. IEEE.  \url{https://doi.org/10.1109/ICCE-China.2017.7991033} 
	
	\item Ken Ikuta, Takuya Kusaka, \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, and Thomas H. Austin. `` Estimation of computational complexity of Pollard's rho method based attack for solving ECDLP over Barreto-Naehrig curves.'' 32nd International Technical Conference on Circuits / Systems, Computers and Communications (ITC-CSCC), 2017. IEIE. 
	
	\item Ken Ikuta, Sho Joichi, Kazuya Kobayashi, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka and Yasuyuki Nogami. ``A Study on the Parameter Size of the Montgomery Trick for ECDLP.'' International Symposium on Information Theory and its Applications (ISITA), 2018. IEICE. (To appear in IEEE Xplore).
	
	\item Ken Ikuta, Sho Joichi, Kazuya Kobayashi, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka and Yasuyuki Nogami. ``A Study on the Parameter of the Distinguished Point Method in Pollard's Rho Method for ECDLP.'' International Symposium on Information Theory and its Applications (ISITA), 2018. IEICE. (To appear in IEEE Xplore).
	
	\item Takuya Kusaka, Sho Joichi, Ken Ikuta, \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, Satoshi Uehara, Nariyoshi Yamai and Sylvain Duquesne. ``Solving 114-Bit ECDLP for a Barreto-Naehrig Curve.'' In: Kim H., Kim DC. (eds) Information Security and Cryptology (ICISC),  2017. Lecture Notes in Computer Science, vol 10779. Springer, Cham. \url{https://doi.org/10.1007/978-3-319-78556-1_13}.
	
	\item Taehwan Park, Hwajeong Seo, Garam Lee, \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami, Howon Kim. ``Parallel Implementations of SIMON and SPECK, Revisited.'' In: Kang B., Kim T. (eds) Information Security Applications (WISA), 2017. Lecture Notes in Computer Science, vol 10763. Springer, Cham. \url{https://doi.org/10.1007/978-3-319-93563-8_24}. (Acceptance Ratio 27/53 $\approx$ 50\%)
	
	\item	Yuta Kodera, Takuya Kusaka, Takeru Miyazaki, \textbf{Md. Al-Amin Khandaker}, Yasuyuki Nogami and  Satoshi Uehara. ``An Efficient Implementation of Trace Calculation over Finite Field for a Pseudorandom Sequence.'' Fifth International Symposium on Computing and Networking (CANDAR), 2017. IEEE. \url{https://doi.org/10.1109/CANDAR.2017.86}.
	
	\item Akihiro Sanada, Yasuyuki Nogami, Kengo Iokibe, \textbf{Md. Al-Amin Khandaker}. ``Security analysis of Raspberry Pi against Side-channel attack with RSA cryptography.'' IEEE International Conference on Consumer Electronics-Taiwan (ICCE-TW), 2017. IEEE.  \url{https://doi.org/10.1109/ICCE-China.2017.7991108} 
	
\end{enumerate}
\vspace{10mm}
\large
\item Domestic conferences
\begin{enumerate}
	
	\item \textbf{Md. Al-Amin Khandaker}, Hirotaka Ono, Yuki Nanjo, Takuya Kusaka and Yasuyuki Nogami. ``Efficient Optimal-Ate Pairing on BLS-12 Curve Using Pseudo 8-Sparse Multiplication.'' Computer Security Symposium  (CSS),  2017, CD-ROM (3E1-4). 
	
	\item \textbf{Md. Al-Amin Khandaker} and Yasuyuki Nogami. ``Efficient Scalar Multiplication by Skew Frobenius Map with Multi-Scalar Multiplication for KSS Curve.'' Symposium on Cryptography and Information Security (SCIS),  2017, CD-ROM (B1-3). 
	
	\item Yuki Nanjo,  \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, Yasuyuki Nogami. ``A Study on a Construction Method of Degree 18 Extension Field for Efficient Pairing over KSS Curves.''  Computer Security Symposium  (CSS),  2018, CD-ROM (??). 
	
	\item  Hirotaka Ono, \textbf{Md. Al-Amin Khandaker}, Yuki Nanjo, Toshifumi Matsumoto, Takuya Kusaka and Yasuyuki Nogami. ``An Implementation and Evaluation of ID-based Authentication on Raspberry Pi with Pairing Library.'' Symposium on Cryptography and Information Security (SCIS),  2018, CD-ROM (4D2-1).  
	
	\item Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Yuta Kodera and Yasuyuki Nogami. ``Implementation method of the pairing over BN curve using two type of extension fields.'' Symposium on Cryptography and Information Security (SCIS),  2018, CD-ROM (4D2-3).
	
	\item Yuki Nanjo,  \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka, and  Yasuyuki Nogami. ``The relation between the efficient sextic twist and constant of the modular polynomial for BN curve.'' Computer Security Symposium  (CSS),  2017, CD-ROM (3E1-3). 
	
	\item  Norito Jitsui, Yuki Nanjo, \textbf{Md. Al-Amin Khandaker}, Takuya Kusaka and Yasuyuki Nogami. ``	Efficient Elliptic Scalar Multiplication for Pairing-Based Cryptography over BLS48.'' Symposium on Cryptography and Information Security (SCIS),  2018, CD-ROM (3B4-1).  
	
		
%``KSS曲線に対するマルチスカラー乗算を用いたSkew Frobeniusマップによる効率的なスカラー倍計算.'', SCIS 2017. 
\end{enumerate}
\normalsize
\end{itemize}

